A recipe for extremely reproducible enrichment analysis (and why we need it)

### 2023-05-04 manuscript.Rmd
Fig2 now reproducible

![Figure 2. The five pillars of computational reproducibility.](img/pillarsV2.png "The five pillars of computational reproducibility. .")

@@

grViz("digraph flowchart {
      node [fontname = Helvetica, shape = rectangle]
      tab1 [label = '@@1']
      tab2 [label = '@@2']
      tab3 [label = '@@3']
      tab4 [label = '@@4']
      tab5 [label = '@@5']
      tab6 [label = '@@6']
      tab1 -> tab2 -> tab3 -> tab4 -> tab6;
      tab3 -> tab5 -> tab6 }
      [1]: 'Fetch RNA-seq from DEE2'
      [2]: 'Quality control'
      [3]: 'Differential expression'
      [4]: 'Over-representation analysis'
      [5]: 'Functional class scoring'
      [6]: 'Euler diagram'
")

>>>>

```{r,5pillars,fig.cap="Figure 2. The five pillars of computational reproducibility.",echo=FALSE,fig.height=6}

library("RColorBrewer")
cols <- brewer.pal(5, "Set2")
cols2 <- adjustcolor( cols, alpha.f = 0.7)
plot(0,type='n',axes=FALSE,ann=FALSE, xlim=c(0, 10), ylim=c(0, 8.5))
polygon(c(0,1.8,1.8,0),c(1,1,6,6), col=cols2[1], border = NA)
polygon(c(2,3.8,3.8,2),c(1,1,6,6), col=cols2[2], border = NA)
polygon(c(4,5.8,5.8,4),c(1,1,6,6), col=cols2[3], border = NA)
polygon(c(6,7.8,7.8,6),c(1,1,6,6), col=cols2[4], border = NA)
polygon(c(8,9.8,9.8,8),c(1,1,6,6), col=cols2[5], border = NA)
polygon(c(-0.2,10,10,-0.2),c(-0.4,-0.4,0.8,0.8),col="lightgray", border = NA)
polygon(c(-0.2,5,10),c(6.5,8.5,6.5),col="lightgray", border = NA)
points( c(0.9,2.9,4.9,6.9,8.9) , c(4.5,2.5,4.5,2.5,4.5), pch=19,cex=18,col=cols )
text(5,7,lab="Five pillars of reproducible computational research", cex=1.5)

labs <- c("Version\ncontrol &\npersistent\ncode sharing",
  "Compute \nenvironment \ncontrol",
  "Literate\nprogramming",
  "Documentation",
  "FAIR &\npersistent\ndata sharing")

text( c(0.9,2.9,4.9,6.9,8.9) , c(4.5,2.5,4.5,2.5,4.5) , lab=labs)
text( 9, -0.2 , lab=expression(italic("created by Mark Ziemann")),cex=0.5)

@@

library("DiagrammeR")
grViz("digraph flowchart {
      node [fontname = Helvetica, shape = rectangle]
      tab1 [label = '@@1']
      tab2 [label = '@@2']
      tab3 [label = '@@3']
      tab4 [label = '@@4']
      tab5 [label = '@@5']
      tab6 [label = '@@6']
      tab1 -> tab2 -> tab3 -> tab4 -> tab6;
      tab3 -> tab5 -> tab6 }
      [1]: 'Fetch RNA-seq from DEE2'
      [2]: 'Quality control'
      [3]: 'Differential expression'
      [4]: 'Over-representation analysis'
      [5]: 'Functional class scoring'
      [6]: 'Euler diagram'
")
